Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation

### 2022-01-15 paper/paper.Rmd
add some text on models

>>>>

Details of geostatistical spatiotemporal models for each survey type:

The hard bottom long-line (HBLL) survey counts the number of individual fish caught for a given number of hooks (median = 450).
<!-- This hook count can be transformed into densities using the average hook spacing (0.0024384 km) and an estimate of the catch radius (0.009144 km). -->
This data was fit with log hook count included as on offset and a negative bionomial type 2 (`nbinom2`) distribution.
Synoptic trawl surveys (SYN) collect total biomass per area swept giving an estimate of biomass density for each species.
This data was fit with a Tweedie distribution to account for positive continuous values that also contain zeros. 
Both model types include an intercept for each year, independent and identically distributed (IID) spatiotemporal random fields, and a fixed spatial random field (IF THIS IS THE PACKAGE DEFAULT?).
